% David Gurevich resume
% Accurate as of: 2022-12-01

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage{tabularx}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fontawesome}
\usepackage[pdftex, hidelinks]{hyperref}
\usepackage{fancyhdr}

\usepackage[charter]{mathdesign} % Bitstream Charter
% \usepackage{newpxtext,newpxmath} % Palatino

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.50in}
\addtolength{\evensidemargin}{-0.50in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNoBullet}[2]{
  \item[]\small{
    \hspace{-9pt}\textbf{#1}{: #2 \vspace{-6pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item[]
  \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \hspace{-10pt}\textbf{#1} & #2 \\
      \hspace{-10pt}\textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubsubheading}[1]{
    \vspace{-25pt}\item[]
    \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
        \hspace{-10pt}\emph{\textbf{\small#1}}
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubheadingA}[2]{
  \vspace{-1pt}\item[]
  \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \hspace{-10pt}\textbf{#1} & #2 \\
    \end{tabular*}\vspace{-24pt}
}

\newcommand{\resumeSubheadingB}[2]{
  \vspace{-10pt}\item[]
  \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \hspace{-10pt}\textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItemNoBullet{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% custom commands
\newcommand{\shorterSection}[1]{\vspace{-10pt}\section{#1}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{table}[]
    \begin{tabularx}{\textwidth}{Xr}
        \Huge{David Gurevich}
        &
        \begin{tabular}[c]{@{}r@{}}
            \href{mailto:dgurevich@uwaterloo.ca}{\texttt{dgurevich@uwaterloo.ca}} \\
            \href{tel:14164140515}{\texttt{(416) 414 0515}} \\
            \href{http://gurevich.ca}{\texttt{gurevich.ca}}
        \end{tabular}
        \vspace{-10pt}
    \end{tabularx}
\end{table}

%-----------SKILLS-----------------
\shorterSection{Technical Skills}
\resumeSubHeadingListStart
\small
\item{
        \textbf{Languages}{: Python, C++, C, Rust, MATLAB, Scheme, SQL, Shell scripting}
    } \vspace{-5pt}

\item{
        \textbf{Libraries}{: NumPy, SciPy, Pandas, PyTorch, TensorFlow, sklearn, Matplotlib, Flask, OpenCV, FFTW, CTypes}
    } \vspace{-5pt}

    \resumeSubHeadingListEnd

    %-----------EDUCATION-----------------
    \vspace{-3pt}
\shorterSection{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Waterloo}{Waterloo, ON}
      {Bachelor of Mathematics in Computer Science and Computational Mathematics}{Expected Graduation: April 2025}
    \vspace{1pt}
    \resumeItem{\vspace{-5pt}
        \emph{\textbf{Quickest Change Detection}}: Performed supervised research on non-parametric quickest changepoint detection of high-dimensional data on low power systems.
    }
    \resumeItem{\vspace{-5pt}
        \emph{\textbf{Spiking Neural Networks}}: Investigated ability of spiking neural networks in solving certain classes of partial differential equations on neuromorphic hardware.
    }
    \resumeItem{\vspace{-5pt}
        \emph{\textbf{LLM Research}}: Investigated the efficacy of LLM's like LLaMA in performing graph clustering tasks.
    }
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\vspace{-2pt}
\shorterSection{Experience}
 \resumeSubHeadingListStart
    \resumeSubheading
      {Enlighted -- Siemens AG}{Waterloo, ON}
      {IoT Research Intern}{January 2024 - April 2024}
    \resumeItemListStart
    \resumeItem{Independently researched and developed a data-efficient \textbf{LSTM}-based approach to perform RSSI-based localization of Bluetooth Low Energy (BLE) assets using \textbf{TensorFlow}.}
      \resumeItem{New machine learning-based approach achieves accuracy of 2 metres, compared to 4.5 metre accuracy of previous solution, with improved trajectory estimation and decreased time delay.}
      \resumeItem{Developed data-driven \textbf{channel estimation} utilities to facilitate conversion from signal strength (dBm) to distance.}
      \resumeItem{Performed mathematical analysis on optimal estimators (CRLB) and filters (Kalman) to establish benchmarks.}
    \resumeItemListEnd
    \vspace{-10pt}
    \resumeSubheading
      {MathWorks, Inc}{Glasgow, Scotland}
      {Software Engineer in Test Intern}{May 2023 - August 2023}
      \resumeItemListStart
      \resumeItem{Improved open-source UHD hardware simulator with \textbf{Python}, enriching its versatility for cost-effective testing.}
        \resumeItem{Enhanced the \textbf{C++} based high-speed data acquisition interface, ensuring accurate performance benchmarking and optimal system evaluation.}
        \resumeItem{Consolidated several RF processing chains to reduce the number of \textbf{FPGA} bitstreams required for building and testing MATLAB Wireless Testbench by 50\%, resulting in a 4+ hour reduction in daily build time.}

      \resumeItemListEnd
      \vspace{-5pt}
    \resumeSubheading
      {Microchip Technologies, Inc}{Toronto, ON}
      {Software Engineering Intern}{September 2022 - December 2022}
      \resumeItemListStart
        \resumeItem{Responsible for porting and documenting SmartHLS FPGA high-level synthesis build system from Makefiles to \textbf{Python}, allowing for Windows compatibility and improved maintainability.}
        \resumeItem{Implemented improvements and developed data structures in \textbf{C++} which eliminated non-determinism in LLVM-based synthesis from C/C++ to Verilog, allowing for improved integration testing.}
      \resumeItemListEnd
      \vspace{-5pt}

    \resumeSubheading
      {Applied Mind, Inc}{Ottawa, ON}
      {Software Development Intern}{January 2022 - April 2022}
      \resumeItemListStart
      \resumeItem{Performed novel research to design and implement sensor fusion algorithms (using \textbf{Kalman filter}, TDOA) in \textbf{Python} to eliminate error in RF emitter location estimates from 2 meters to 0.5 meters.}
      \resumeItem{Designed and implemented high-speed data streaming application for \textbf{embedded Linux} system in \textbf{Rust} within soft real-time performance constraints.}
      \resumeItemListEnd
      \vspace{-5pt}
      
    \resumeSubheading
      {Applied Mind, Inc}{Ottawa, ON}
      {Embedded Software Development Intern}{May 2021 - August 2021}
      \resumeItemListStart
      \resumeItem{Developed multithreaded radio signal acquisition software in \textbf{Rust} to receive and process LTE signals at over 60 MS/s.}
      \resumeItem{Made use of \textbf{DMA} and \textbf{CPU caching} in order to transfer received data from FPGA to processor at over 1 GB/s.}
      \resumeItem{Designed and deployed custom Continuous Integration workflow for embedded software using GitHub Actions.}
      \resumeItem{Implemented Linux userspace drivers in \textbf{Rust} and \textbf{C} to interface with radios and jitter attenuators over SPI and I2C.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
% \shorterSection{Projects}
%   \resumeSubHeadingListStart
%      \vspace{5pt}
%   \resumeSubItem{\href{https://github.com/davidgur/3d-sound-synthesis}{3D Sound Synthesis}}
%   {Localize audio to a particular location around the listener. \\
%       \emph{C++ (STL, FFTW, CMake), MATLAB}
%         \vspace{-5pt}
%         \begin{itemize}
%             \item Designed a custom DSP algorithm (in C++) for 3D sound synthesis, given a position on the unit sphere.
%         \end{itemize}
%      }
%      \vspace{5pt}
%      \resumeSubItem{Cross-Correlation Fluid Flow Meter}
%      {Low-cost signal acquisition and processing system for ultrasonic fluid flow measurement.\\
%          \emph{Python (NumPy, Matplotlib, SciPy), C++, MATLAB}
%         \vspace{-5pt}
%         \begin{itemize}
%             \item Developed high throughput, multi-threaded \textbf{Python} application for acquisition and processing of ultrasonic signals within strict operational requirements.
%         \end{itemize}
%      }
%   \resumeSubHeadingListEnd




\end{document}
